A GPU Sonar Simulator for Automatic Target Recognition

### 2014-05-12 Simulator/article.tex
la2pdf commit - 2014:05:13	01:45:17	(Tue13.May)

Finally the relevant part of the scene is projected onto the image plane with a projection matrix $\P$. There are two main types of projection, perspective and orthographic. Perspective projection scales all $x$ and $y$ coordinates inversely with the distance to the objects to create a sense of perspective in the image. Orthographic projection, on the other hand, maps all the scene's vertices to a squared cube where each dimension has the range [-1,1]. This will render all objects equally large whether they are in the distance or up close. Its projection matrix is defined as
\begin{align}
\P = \left(\begin{matrix}
\frac{2}{r-l}  &  0              &  0              &  -\frac{r+l}{r-l} \\
0              &  \frac{2}{t-b}  &  0              &  -\frac{t+b}{t-b} \\
0              &  0              &  \frac{-2}{f-n} &  -\frac{f+n}{f-n} \\
0              &  0              &  0              &  1
\end{matrix}\right)
\end{align}
where $l,r,b,t,n$ and $f$ are left, right, bottom, top, near and far boundaries of the projection plane, respectively.
\begin{align*}
l &= x_\text{min}  &  r &= x_\text{max}\\
b &=   &  t &= \\
f &=   &  n &= 
\end{align*}

>>>>

Finally the relevant part of the scene is projected onto the image plane with a projection matrix $\P$. There are two main types of projection, perspective and orthographic. Perspective projection scales all $x$ and $y$ coordinates inversely with the distance to the objects to create a sense of perspective in the image. Orthographic projection, on the other hand, maps all the scene's vertices to a squared cube where each dimension has the range [-1,1]. This will render all objects equally large whether they are in the distance or up close. Its projection matrix is defined as
\begin{align}
\P = \left(\begin{matrix}
\frac{2}{r-l}  &  0              &  0              &  -\frac{r+l}{r-l} \\
0              &  \frac{2}{t-b}  &  0              &  -\frac{t+b}{t-b} \\
0              &  0              &  \frac{-2}{f-n} &  -\frac{f+n}{f-n} \\
0              &  0              &  0              &  1
\end{matrix}\right)
\end{align}
where $l,r,b,t,n$ and $f$ are the left, right, bottom, top, near and far boundaries of the projection plane, respectively. They define the window through which we observe our scene. We want this adapted to perfectly fit the specified image size. This is straightforward for left and right since it matches the $x$-axis
\begin{align}
l &= x_\text{min}  &  r &= x_\text{max}
\end{align}
For the near and far limits one simply needs to make sure the scene will fit in it
\begin{align}
b &=   &  t &= \\
f &= 0.1   &  n &= 200 
\end{align}
How to set the bottom and top bounaries can be inferred from \Fig{camera_top_bottom}. First we define an origin vector that points to the center of the image
\begin{align}
\vec o &= \left[\frac{x_\text{min}+x_\text{max}}{2}, \frac{y_\text{min}+y_\text{max}}{2}, \frac{z_\text{min}+z_\text{max}}{2} \right]\T,
\end{align}
and the distance from the image origin to its $y$-boundaries is given as
\begin{align}
\Delta y &= \frac{y_\text{max} - y_\text{min}}{2}.
\end{align}
To find the nearest and farthest point in the image that will be part of the projected scene, $\alpha$ and $\beta$, we must consider the seafloor rotation angle around the $x$-axis, $\Phi_x$ 
\begin{align}
\alpha &= \vec 0 - \left[0, \Delta y, \Delta y \times \arctan\Phi_\text{x} \right]
\end{align}
